The promise of community driven preprints in ecology and evolution

### 2024-04-30 ms/ms.qmd
Fix fig 2 to have some colour

# Load packages
#install.packages("pacman")
remotes::install_github("lmullen/genderdata")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick)

@@

##---------------------##
# Articles on EcoEvoRxiv over time
##---------------------##

@@

p3_pub <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))

>>>>

# Load packages
#install.packages("pacman")
#remotes::install_github("lmullen/genderdata")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot, magick)

@@

  dates_preprints <- range(preprints$preprint_published_date)
##---------------------##
# Articles on EcoEvoRxiv over time
##---------------------##

@@

p3_pub <- preprints  %>% ggplot(aes(x = oa_status, fill = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14)) + scale_fill_manual(values = c("bronze" = "#9b6023", "gold" = "#ffd700", "green" = "#008000", "hybrid" = "#6fa8dc", "NA" = "grey", "closed" = "black"))
